---
title: "Jellyfish_atlantis"
author: "Hem Nalini Morzaria-Luna"
format: html
editor: visual
---

## Jellyfish

Modify the current Gelatinous zooplankton group into two, one for Aurelia and other gelatinous zooplankton using data for Green et al. In prep.

```{r}
#| label: load-packages
#| include: false
source("libraries.R")
```

Used landcover classes at 30 m resolution. Development classes were based on the NCCOS' Coastal Change and Analysis Program (C-CAP, 2006 analysis year). Nationally standardized, raster-based inventories of land cover for the coastal areas of the U.S. Data are derived, through the Coastal Change Analysis Program, from the analysis of multiple dates of remotely sensed imagery. https://coast.noaa.gov/digitalcoast/tools/lca.html. Land classification scheme https://coast.noaa.gov/data/digitalcoast/pdf/ccap-class-scheme-regional.pdf

Calculate %land cover classes per

```{r}
#| echo: false

atlantis.polygons <- st_read(here("inputs","bgm_Puget_Sound_89b_0p0001_NAD83.shp"))

#this is the area selected for data 
land.cover.area <- st_read(here("inputs","Job736234_2006_CCAP_index.shp"))

world <- ne_countries(scale = "large", returnclass = "sf")

#check that the land cover area matches Atlantis polygons
ggplot(data = world) +
geom_sf(data = land.cover.area) +
geom_sf(data = atlantis.polygons)


land.cover.raster <- raster(here("inputs","Job736234_2006_CCAP.tif"))

#crop.raster <- st_crop(land.cover.raster, atlantis.polygons)

#DEM boundaries of watershed
#buffer 200 m from the shoreline, is catchment


#Agricultural, also Grassland (8)
land.cover.raster.ag <- land.cover.raster
land.cover.raster.ag[land.cover.raster.ag>=7] <- 0
land.cover.raster.ag[land.cover.raster.ag<=5] <- 0

land.cover.raster.ag.df <- as.data.frame(land.cover.raster.ag, xy = TRUE)

land.cover.plot <- ggplot() +
  geom_raster(data = land.cover.raster.ag.df , aes(x = x, y = y, fill = Job736234_2006_CCAP)) + 
  coord_quickmap() 

land.cover.plot

#Agricultural categories (6) cultivated crops and (7) pasture
land.cover.raster.ag <- land.cover.raster
land.cover.raster.ag[land.cover.raster.ag>=8] <- 0
land.cover.raster.ag[land.cover.raster.ag<=5] <- 0

land.cover.raster.ag.df <- as.data.frame(land.cover.raster.ag, xy = TRUE)

ag.plot <- ggplot() +
  geom_raster(data = land.cover.raster.ag.df , aes(x = x, y = y, fill = Job736234_2006_CCAP)) + 
  coord_quickmap() 


#Development categories High (2), Medium (3), Low (4)
land.cover.raster.dev <- land.cover.raster
land.cover.raster.dev[land.cover.raster.dev>=6] <- 0

land.cover.raster.dev.df <- as.data.frame(land.cover.raster.dev, xy = TRUE)

dev.plot <- ggplot() +
  geom_raster(data = land.cover.raster.dev.df , aes(x = x, y = y, fill = Job736234_2006_CCAP)) + 
  coord_quickmap() 

dev.plot
```

Model from Green et al. In prep,

```{r}
#read in dataset 
jellydf <- read_excel(here("inputs","Revised_Compiled_Data.xlsx"))

pres.sp <- c("Cyanea", "Aurelia", "Aequorea", "Phacellophora", "Pleurobrachia", "Mitrocoma", "Clytia")
factor.vars  <- c("Basin","Site","Month", "Geomorph")#Convert Variables to Factors and Numerics
numeric.vars <- c("Pct_Ag","Pct_Dev","CTD_max_cast_temp_C", "CTD_ave_cast_salinity_PSU", "CTD_max_cast_depth_m", "CTD_min_cast_salinity_PSU")


new.df <- jellydf %>% 
 dplyr::mutate(dplyr::across(dplyr::all_of(pres.sp), 
                ~ sub("0", "Absent", .))) %>% 
 dplyr::mutate(dplyr::across(dplyr::all_of(pres.sp), 
                ~ sub("1", "Present", .))) %>% 
 dplyr::mutate(dplyr::across(dplyr::all_of(factor.vars), 
                ~ as.factor(.))) %>% 
 dplyr::mutate(dplyr::across(dplyr::everything(.), 
                ~ sub("N/A", NA_character_, .))) %>% 
 dplyr::rename(Pct_Ag = `Microbe_Pct Ag Catch`, Pct_Dev = `Microbe_Pct Dev Catch`) %>% #landscape variables
 dplyr::mutate(dplyr::across(dplyr::all_of(numeric.vars), #environmental variables
                ~ as.numeric(.)))   %>% 
 dplyr::mutate(total = Pct_Dev + Pct_Ag) %>%   
 dplyr::mutate(scalemaxtemp = scale(CTD_max_cast_temp_C), 
               scaleavesal = scale(CTD_ave_cast_salinity_PSU),
               scaleminsal = scale(CTD_min_cast_salinity_PSU),
               scaledepth = scale(CTD_max_cast_depth_m),
               #standardized site level variables 
               scaleag = scale(Pct_Ag), 
               scaledev = scale(Pct_Dev),
               scaletotal = scale(total))


#Aequorea
AQmodel <- glmmTMB(Aequorea ~ Geomorph + scaletotal + Geomorph*scaletotal + scalemaxtemp + I(scalemaxtemp^2) + scaleavesal + (1|Basin) + ar1(Month-1|Basin), data = jellydf, family = "binomial", na.action = "na.omit")
summary(AQmodel)

#Aurelia 
Amodel <- glmmTMB(Aurelia ~ Geomorph + scaleag + scalemaxtemp + (1|Basin) + ar1(Month-1|Basin), data = jellydf, family = "binomial", na.action = "na.omit")
summary(Amodel)

#Clytia
CLmodel <- glmmTMB(Clytia ~ Geomorph + scaleag + scaleminsal + I(scaleminsal^2) + scaledepth + (1|Basin) + ar1(Month-1|Basin), data = jellydf, family = "binomial", na.action = "na.omit")
summary(CLmodel)
#the results for this model do not line up!

#Cyanea 
Cmodel <- glmmTMB(Cyanea ~ Geomorph + scaletotal + scalemaxtemp + I(scalemaxtemp^2) + scaledepth + (1|Basin) + ar1(Month-1|Basin), data = jellydf, family = "binomial", na.action = "na.omit")
summary(Cmodel)

#Mitrocoma
Mmodel <-glmmTMB(Mitrocoma ~ Geomorph + scaleag + Geomorph*scaleag + scalemaxtemp + scaleavesal + (1|Basin) + ar1(Month-1|Basin), data = jellydf, family = "binomial", na.action = "na.omit")
summary(Mmodel)

#Phacellophora
Pmodel <- glmmTMB(Phacellophora ~ Geomorph + scaledev + Geomorph*scaledev + scalemaxtemp + I(scalemaxtemp^2) + scaleavesal + (1|Basin) + ar1(Month-1|Basin), data = jellydf, family = "binomial", na.action = "na.omit")
summary(Pmodel)

#Pleurobrachia 
PLmodel <-glmmTMB(Pleurobrachia ~ Geomorph + scaleag + scaledepth + I(scaledepth^2) + scaleavesal + (1|Basin) + ar1(Month-1|Basin), data = jellydf, family = "binomial", na.action = "na.omit")
summary(PLmodel)
```

\`\`\`
